---
title: "CBOW+CA"
author: "Richa Singh"
date: "1/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
rm(list = ls())
graphics.off()
```

# Correspondance Analysis 


Correspondence Analysis is a generalized principal component analysis tailored for the analysis of qualitative data. Also commonly known as reciprocal averaging is a multivariate statistical technique proposed by Herman Otto. It is conceptually similar to principal component analysis, but applies to categorical rather than continuous data. In a similar manner to principal component analysis, it provides a means of displaying or summarising a set of data in two-dimensional graphical form.This is a descriptive/exploratory technique designed to analyze simple two-way and multi-way tables containing some measure of correspondence between the rows and columns. The results provide information which is similar in nature to those produced by Factor Analysis techniques, and they allow you to explore the structure of categorical variables included in the table.Originally, ca was created to analyze contingency tables, but, ca is so versatile that it is used with a lot of other data table types.


```{r}
data <- read.csv("export_dataframe.csv")
#row.names(data) <- ("Doc1","Doc2","Doc3","Doc4")
```

```{r}
library(data.table)
(setattr(data, "row.names", c("Doc1", "Doc2", "Doc3","Doc4")))
```

**Heat Map**

A heat map (or heatmap) is a graphical representation of data where the individual values contained in a matrix are represented as colors. 

```{r include=FALSE}
library(data4PCCAR)
library(PTCA4CATA)
library(corrplot)
library(ggplot2)
library(ExPosition)
library(InPosition)
```

```{r}
col4J <- prettyGraphsColorSelection(NCOL(data))
heatMapIJ <- makeggHeatMap4CT(data,
                 colorAttributes = col4J,
                 fontSize.x = 15)
print(heatMapIJ)
```

```{r,include=FALSE}
resCA.sym  <- epCA(data, symmetric = TRUE,graphs = FALSE)
resCA.asym <- epCA(data, symmetric = FALSE,graphs = FALSE)
rescainf <- epCA.inference.battery(data,graphs = FALSE)

Fj.a <- resCA.asym$ExPosition.Data$fj
Fi   <- resCA.sym$ExPosition.Data$fi
Fj   <- resCA.sym$ExPosition.Data$fj

constraints.sym <- minmaxHelper(mat1 = Fi, mat2  = Fj)
constraints.asym <- minmaxHelper(mat1 = Fi, mat2  = Fj.a)
```

```{r}
library(PTCA4CATA)
PlotScree(ev = resCA.sym$ExPosition.Data$eigs, 
          p.ev =  rescainf$Inference.Data$components$p.vals,
          title = 'Drug useby Age data Set. Eigenvalues Inference',
          plotKaiser = TRUE
)
```

## Factor Map for Symmetrical Graph

```{r}
color <-prettyGraphsColorSelection(NROW(data))
baseMap.i1 <- createFactorMap(Fi, constraints = constraints.sym,
                             col.points = color,
                            col.labels = color , cex = 5, text.cex = 4, pch = 20,
                            display.labels = TRUE , alpha.axes = 0.2,alpha.points = 1
) 

label4Map0 <- createxyLabels.gen(1,2,
                                lambda = resCA.sym$ExPosition.Data$eigs,
                                tau = resCA.sym$ExPosition.Data$t )

print(baseMap.i1$zeMap + baseMap.i1$zeMap_dots + label4Map0)
```

```{r}
baseMap.i12 <- createFactorMap(Fi, constraints = constraints.sym,
                             col.points = color,axis1 = 2,axis2 = 3,
                            col.labels = color , cex = 5, text.cex = 4, pch = 20,
                            display.labels = TRUE , alpha.axes = 0.2,alpha.points = 1
) 

label4Map1 <- createxyLabels.gen(2,3,
                                lambda = resCA.sym$ExPosition.Data$eigs,
                                tau = resCA.sym$ExPosition.Data$t )

print(baseMap.i12$zeMap + baseMap.i12$zeMap_dots + label4Map1)
```

```{r}
baseMap.i13 <- createFactorMap(Fi, constraints = constraints.sym,
                             col.points = color,axis1 = 1,axis2 = 3,
                            col.labels = color , cex = 5, text.cex = 4, pch = 20,
                            display.labels = TRUE , alpha.axes = 0.2,alpha.points = 1
) 

label4Map3 <- createxyLabels.gen(1,3,
                                lambda = resCA.sym$ExPosition.Data$eigs,
                                tau = resCA.sym$ExPosition.Data$t )

print(baseMap.i13$zeMap + baseMap.i13$zeMap_dots + label4Map3)
```


## Factor Map for Asymmetrical Graph

```{r}
baseMap.i2 <- createFactorMap(Fi, constraints = constraints.asym,
                             col.points = color,
                            col.labels = color , cex = 5, text.cex = 4, pch = 20,
                            display.labels = TRUE , alpha.axes = 0.2,alpha.points = 1
)
print(baseMap.i2$zeMap + baseMap.i2$zeMap_dots )
```


## Contribution Bars for variables 

```{r}
signed.ctrJ1 <- resCA.sym$ExPosition.Data$cj * sign(resCA.sym$ExPosition.Data$fj)
b003.ctrJ.s.11 <- PrettyBarPlot2(signed.ctrJ1[,1],
                                threshold = 1 / NROW(signed.ctrJ1),
                                font.size = 5,
                                #color4bar = gplots::col2hex(color4drugs), # we need hex code
                                main = 'CA on the MatlabCode data Set: Variable Contributions (Signed)',
                                ylab = 'Contributions',
                                ylim = c(1.2*min(signed.ctrJ1), 1.2*max(signed.ctrJ1))
)
print(b003.ctrJ.s.11)
b004.ctrJ.s.21 <- PrettyBarPlot2(signed.ctrJ1[,2],
                                threshold = 1 / NROW(signed.ctrJ1),
                                font.size = 5,
                                #color4bar = gplots::col2hex(col4J.ibm), # we need hex code
                                main = 'CA on the MatlabCode dataSet: Variable Contributions (Signed)',
                                ylab = 'Contributions',
                                ylim = c(1.2*min(signed.ctrJ1), 1.2*max(signed.ctrJ1))
)
print(b004.ctrJ.s.21)
b004.ctrJ.s.31 <- PrettyBarPlot2(signed.ctrJ1[,3],
                                threshold = 1 / NROW(signed.ctrJ1),
                                font.size = 5,
                               #color4bar = gplots::col2hex(col4J.ibm), # we need hex code
                                main = 'CA on the MatlabCode dataSet: Rows Contributions (Signed)',
                                ylab = 'Contributions',
                                ylim = c(1.2*min(signed.ctrJ1), 1.2*max(signed.ctrJ1))
)
print(b004.ctrJ.s.31)
```

## Summary 


# DiSTATIS

DISTATIS is a new method that can be used to compare algorithms when their outputs consist of distance matrices computed on the same set of objects. The method first evaluates the similarity between algorithms using a coefficient called the RV coefficient. From this analysis, a compromise matrix is computed which represents the best aggregate of the original matrices. In order to evaluate the differences between algorithms, the original distance matrices are then projected onto the com- promise. We illustrate this method with a ???toy example??? in which four different ???algorithms??? (two computer programs and two sets of human observers) evaluate the similarity among faces.


DiSTASIS can't be performed for Bag of words model I think I becuase of the distance metric thingy 







